Adopting agile in the large: motivations, success factors and challenges

### 2014-05-11 journal/article.tex
Work in progress

% Using two models side by side

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P26], and causing tensions on all organizational
levels [P10]. Ongoing projects had been set up with previous development
methods, and the agile methods had to be arranged to fit with them [P8, P29].
A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

@@

@@

@@

>>>>

% Using two models side by side
% Part of the organization is in old mindset

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P1, P26], and causing tensions on all organizational
levels [P10]. Ongoing projects had been set up with previous development
methods, and the agile methods had to be arranged to fit with them [P8, P29].
A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

@@

% Add quote ?
% * Especially higher organizational levels were not using agile --> Problem
% [P3]
% Scrum still exists mostly in a way that avoids conflict with the larger
% corporate organization, and there has been little progress in addressing larger,
% organizational impediments.

% [P18]
% Real Agile teams will experience resistance when they start working with
% non-Agile interfaces. Lack of understanding in ‘why to help create a cadence?’,
% ‘why involve the customer more?’ will cause resistance in the change process.

% --> ``Part is in the old mindset''
% * Problem: Management attempts to use a ``resource pool'' of individuals rather than coordinating teams
% [P6]
% we face the constant threat that restructuring and the instinct from management
% to track and leverage resources at the individual level (for example
% organization-wide resource pools) will destroy the team dynamic and adversely
% affect productivity.

\subsubsection{Integrating other functions than development to agile}

Agile methods are typically understood through a set of activities closely
related to software development. Cases describe how development teams were
typically the first entities in the organization that were considered when
introducing agile [P2, P17, P31, P38]. However, development operates in a larger
context, and will need to interface with other organizational functions.
Challenges were faced when exposing other parts of the organization to the agile
mode, and functions that were further away from development were resistant to
change [P2, P18, P31]. A tension was growing between development and broader
roles in the organization [P1]. The full beenfits of the transformation would
not be attained unless the entire organization was set to work along the same
paradigm [P18, P42].

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Marketing was a particularly frequently
mentioned group [P5, P17, P28, P31, P38, P45, P48]. Other groups involved in the
whole of product delivery were sales [P17, P31], infrastructure and operations
[P10, P45, P46, P50], user experience and design [P9, P10, P28], documentation
[P28], legal [P10], security [P10], customer services [P48], and finance [P48].
All of these groups were reported to be affected on some level by the agile
transformation.
% separate QA [P3], --> Later
% human resources --> Later

Agile affects timings in the software delivery lifecycle which caused two types
of problems. Firstly, the iterativeness of agile models was problematic when
interfacing with other functions. Iterativeness changed the pace of delivery
[P17], and forced design to focus on a shorter scope [P15]. Various groups
feeding and supporting development had earlier committed once to a long term
plan, but in the new arrangement they needed to adjust to incremental delivery
[P48].
Especially user experience (UX) and interaction designers did not welcome an
incremental model [P6], and were struggling with maintaining the big picture in
design while working in iterations [P9, P10].
The infrastructure and operations teams were falling behind due to the increased
delivery speed of development teams, and they were forced to update their way of
working [P46, P50].

Federoff and Courage [P15] elaborate on the user experience team's problems
with the short time horizons of Scrum. Previously the UX team had supplied
development with designs within a long release cycle, but Scrum required
completing features within weeks. The problem was that that the UX work required
a holistic view instead of an incremental one, and the design process did not
fit well into the time frame of a sprint. The UX team was overloaded and
discontent, but the situation was fixed by refining the schedule for interations
with development teams. [P15, P28]

The second type of problems was that some release activities would inevitably
have a long lead time but required committing to a set of functionalities in
good time. The agile models' emphasis on short time horizon and flexibility in
prioritization did not mix well with such activities.
For instance, it would take time to prepare printed marketing material and press
releases, but they needed to accurately present the upcoming features of the
product [P38].

Maples [P31] describes that marketing needed three months for preparing the
product launch, but the agile process allowed development to keep changing the
content of the product. As a result marketing was struggling with creating
material and campaigns without knowing the exact product features. Further, the
processes of acquiring export clearances and licensing authority required that
the the feature set of the product was known well on beforehand [P31].
As a result of these requests development felt that their process was being
slowed down. The issues were solved by agreeing on that marketing could at any
time request a release in 90 days, and development would be able to commit to a
fixed feature set to be delivered [P31].

% --

Some cases reported that development efforts were controlled on a top level by a
project management office (PMO). The PMO was described as entrenched in a
waterfall paradigm, and the top-level rigidity was causing friction in the
agile adoption [P3, P6]. The PMO was seen as a hub and bottleneck controlling
all aspects of projects, and its central structure had to be dismantled for
the organization to become agile [P46].

Problems in adopting agile were even showing in functions outside the software
delivery lifecycle. A support function that was particularly mentioned to
have issues in agile adoption was human resouces (HR).

@@

"C: Adapting non-development parts of organization to agile"

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MARKETING NEEDS TO KNOW ON BEFOREHAND WHAT WILL BE RELEASED
% 
% 
% * Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
% * Problem: Sales and marketing organization had a different vision of the product
% * Problem: Product marketing was not collaborative, and in old mindset
% * Problem: Requirements --> user stories more granular and prioritized
% [P31]
% After several months of working on the new products, the Agile teams “drained”
% the backlog.   For a while, they kept busy working on new user stories that came
% directly from the strategic customer.  This began to lead to a disconnect
% between what the marketing and sales organizations believed to be the overall
% direction of the product, and the actual direction it was taking based on the
% needs of a single customer. It was clearly time for a regroup, and the
% engineering team pushed back on the MRD.  They were in full production mode
% using Agile and they needed more granular, prioritized user stories to fuel
% their efforts.  The teams needed product marketing to be more collaborative in
% the decomposition of the requirements. This was a totally foreign concept for
% the product marketing team. They had approached the relationship with
% engineering as a “black box” – high level requirements went in, and something
% eventually came out (usually late, and sometimes off the mark on what they
% expected).
% 
% 
% * Challenge: Accomodate time for export clearance
% * Challenge: Acquire third-party licensing authority --> prior to product release
% * Challenge: These processes will remain traditional
% * Challenge: Marketing needs some lead time
% * Enablement activities (sales materials, training)
% * These steps take time, but they are part of the product lifecycle
% * Challenge: Must know beforehand what will be in the product
% [P31]
% While changing our process in the front end of the value chain began to yield
% success, we discovered that there was also a traditional wall at the back end:
% our product release process.
% While the Agile approach enables teams to be flexible with regard to
% prioritization, and very adaptive to changing market conditions and customer
% needs, there are certain “laws of physics” required to release commercial
% product that cannot be altered. For example, the time required to acquire export
% clearance or to acquire third-party licensing authority prior to product
% release.  As a vendor that makes products that must be marketed, sold and
% implemented, there are several traditional processes that are involved in
% releasing our products to market.
% 
% First there are the regulatory requirements such as export compliance relative
% to exporting code with certain levels of encryption,  then there are the
% marketing launch plans (demand generation campaigns, collateral, Web site,
% public relations), and finally, the field enablement activities (sales
% materials, training).  All these initiatives take time, and they cannot begin
% without knowledge of exactly what is going to be in the product.
% 
% 
% * Problem: Marketing had to know on beforehand what will be in the release
% * Problem: Business went with requiring a fixed delivery date and a fixed feature set
% [P31]
% Serious friction arose. The development teams became frustrated because they
% felt marketing and the NPI process was stalling their progress and throwing up
% barriers against the core principles they had adopted.  Marketing, who needed to
% begin prepping for the launch of the product about three months before the
% actual date, found themselves struggling to message and develop materials and
% campaigns without a clear understanding of the features and functionality that
% would actually be “ready” on the release date. And, the NPI group could not
% apply for export compliance nor could they request any third party license
% authorization without knowing what was actually going to be in the product.
% 
% 
% * Solution: Development and product marketing work together
% * Solution: Product marketing can require a release to be completed in 90 days
% [P31]
% What we instituted was what we call an “Iron Triangle.” The concept is that at
% some number of sprints out before a release, we would commit to delivering a
% fixed set of features and functionality  at a certain date.  Of course, there
% was always the opportunity for us to deliver more than what we committed to, 
% but we absolutely had to deliver the set features by the set date.
% 
% If  product marketing wants to release product for any reason they can “declare”
% a release date, and  we’re able to lock the current feature set and have  the
% code ready to release within two sprints of the date they declare the release
% necessary.

@@

REQUIREMENT AND MRD COMMUNICATION PROBLEMS

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
[P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.
Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* Problem: MRD is not dynamic
* Problem: MRD requirements scoped once a year --> Teams decide for themselves
* Problem: Product marketing team was very disrupted of the requirement of collaboration!
[P31]
Further, the MRD needed to be more dynamic. Because the teams had achieved a
predictable, efficient pace of delivery, scoping the requirements of a release
once a year wasn’t enough to feed the engine.  Without the proper fuel the teams
were left to decide for themselves what new things to work on, driving further
disconnect between the groups. The concept of continuous collaboration
throughout the development cycle was a very disruptive concept for the product
marketing team.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]

* Requirements engineering must be done differently
[P45]
Product teams had to communicate with business management, marketing, and field
services who were not fully prepared for how Scrum and the product teams’
expectations would change their daily work. The process of software requirements
engineering were found to require a major adjustment.
